---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/"
)
options(width=100)
library(utsData)
```

### Introduction

This package provides example datasets of multivariate unevenly spaced time series. The data can be loaded, viewed, plotted, and analyzed using the [uts](https://github.com/andreas50/uts), [utsMultivariate](https://github.com/andreas50/utsMultivariate), and utsTrendSeasonality (coming soon) packages.


### Installation

This package is not yet available on CRAN, but can be installled from GitHub, either using the `R` package [devtools](https://cran.r-project.org/web/packages/devtools/index.html):

```{r, eval=FALSE}
devtools::install_github("andreas50/uts", build_vignettes=TRUE)
devtools::install_github("andreas50/utsMultivariate")
devtools::install_github("andreas50/utsData")
```

or using the `R` package [remotes](https://cran.r-project.org/web/packages/remotes/index.html):

```{r, eval=FALSE}
remotes::install_github("andreas50/uts")
remotes::install_github("andreas50/utsMultivariate")
remotes::install_github("andreas50/utsData")
```

### Sample Code

```{r}

```
