---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/"
)
options(width=100)
library(utsData)
```

### Introduction

This package provides example datasets of multivariate unevenly spaced time series. The data can be loaded, viewed, plotted, and analyzed using the [uts](https://github.com/andreas50/uts), [utsMultivariate](https://github.com/andreas50/utsMultivariate), and utsTrendSeasonality (coming soon) `R` packages.


### Installation

This package is not yet available on CRAN, but can be installled from GitHub, either using the `R` package [devtools](https://cran.r-project.org/web/packages/devtools/index.html):

```{r, eval=FALSE}
devtools::install_github("andreas50/uts", build_vignettes=TRUE)
devtools::install_github("andreas50/utsMultivariate")
devtools::install_github("andreas50/utsData")
```

or using the `R` package [remotes](https://cran.r-project.org/web/packages/remotes/index.html):

```{r, eval=FALSE}
remotes::install_github("andreas50/uts")
remotes::install_github("andreas50/utsMultivariate")
remotes::install_github("andreas50/utsData")
```

### Sample Code

```{r co2_plot, fig.width=8, fig.height=4, echo=c(1, 3:5), dev="svg"}
# Mauna Loa atmospheric CO2 concentration
par(mai=c(0.5, 0.5, 0.2, 0.2))
plot(co2_ml)
# Most consecutive observations are one month apart
table(round(diff(time(co2_ml)) / 365 * 12))
```

```{r grapes_plot, fig.width=8, fig.height=4, echo=c(1:2, 4:8), dev="svg"}
# Grape harvest dates (relative to August 31st) for Bordeaux region
# -) observations less than 2 years apart are connected by a line in the polot
par(mai=c(0.5, 0.5, 0.2, 0.2))
plot(grapes$Bordeaux, max_dt=dyears(2), type="o", cex=0.5)
# Same, but plot 20-year two-sided rolling average
if (requireNamespace("utsOperators", quietly=TRUE)) {
  plot(utsOperators::rolling_apply(grapes$Burgundy, width=dyears(20), FUN=mean, align="center"))
}

```
